Weight Lifting Exercise Dataset
========================================================

## Loading the data
Loading the data and necessary Packages
```{r}
library(caret)
train<-read.csv("train.csv",na.strings=c("NA",""))
test_data<-read.csv("test.csv",na.strings=c("NA",""))
```
## Preprocess the data
checking which columns in the data have a lot of missing values. 
```{r}
colums_count_of_missing_values <- colSums(is.na(train))
```
Taking only those columns which have no missing values
```{r}
train_good<-train[,(colums_count_of_missing_values==0)]
test_good<-test_data[,(colums_count_of_missing_values==0)]
```
Removing other unncessary columns from dataset
removing bad columns - "X","user_name","raw_timestamp_part_1","raw_timestamp_part_2","cvtd_timestamp","new_window"

```{r}
train_proc<-subset(train_good,select=-c(1:6))
test_proc<-subset(test_good,select=-c(1:6))
```

Splitting Data into training and test set for building the model With a 80:20 Split

```{r}
set.seed(32423)
inTrain<- createDataPartition(y=train_proc$classe,p=.8,list=FALSE)
training<-train_proc[inTrain,]
testing<-train_proc[-inTrain,]
```
## Training The model
This is a classification model therefore training the model using GBM. Using repeated cross validation:

```{r}
modelFit<- train(classe~.,data=training,trControl=trainControl(method="repeatedcv",number=2,repeats=2, allowParallel=TRUE) ,method="gbm",verbose=FALSE)
```

## Predicting the data and Checking accuracy on testing set
```{r}
pred<-predict(modelFit,testing)
conmat <- confusionMatrix(pred,testing$classe)
conmat$table  
accuracy<-postResample(pred,testing$classe)[[1]]
out_of_sample_error<-(1-accuracy)*100
```
the accuracy comes out to be: 98.9% and the out of sample error is 1.04%
## Predicting on given data set
```{r}
predict_final<-predict(modelFit,test_proc)
predict_final
```